---
title: 'Peer-graded Assignment: Course Project: Shiny Application and Reproducible
  Pitch'
author: "Ridzuan Mohamad"
date: "7/7/2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This is a Project for week 4 under Coursera Data Science Specialization Programme.
It has two parts which covered:- 

1. Shiny for web application.<br>https://ridzuanmo.shinyapps.io/mpg_consumption_analysis/
   
2. Slidify for pitch presentation about the application.<br>http://rpubs.com/ridzuanmo/mpg_analysis

## Shiny Application

The application allow users to visualize the relationship between selected variable, mpg and automobiles. The scatter plot show which automobiles and variable consume gas effectively.

- User may select variables such as Weight, Horsepower, Cylinder and Gear.
- User may resize data sample by define the range for QSec (1/4 mile time)

## Dataset

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

However, we only interested at 5 variable as shown in the table below and row name's represent automobiles models.

```{r, echo = FALSE}
summary(mtcars[,c("mpg", "wt", "gear", "cyl", "qsec")])
```

## Plot

The relationship between Weigth, MPG and Automobiles

```{r, warning=FALSE, echo=FALSE}
library(ggplot2)

mtcars$model = sub(" .*", "", rownames(mtcars))
mtcars$model <- factor(mtcars$model)

ggplot(mtcars, aes_string("wt", "mpg")) +
          geom_point(aes(colour = model), size = 4) +
          guides(color=guide_legend(title="Automobiles")) +
          xlab("Weight (1000 lbs)") +
          ylab("Miles/(US) gallon") + 
          ggtitle("MPG vs Weight (1000 lbs) vs Automobiles")
```

